Graphs

### 2023-11-12 graphs/paper.tex
notation

@@

\begin{defn}
  \label{defn:graphs-undirected}
  A graph $(V,E)$ is \emph{undirected} if the binary relation $E$ is symmetric.
\end{defn}

>>>>

\begin{notn}
  The data described in \cref{defn:graphs} can be formalized as a pair that consists of a set of vertices $V$ and a set of edges $E$.
  We write $(V, E)$ to denote a graph with a vertex set $V$ and an edge set $E$.
\end{notn}

@@

\begin{defn}
  \label{defn:graphs-undirected}
  A graph $G = (V,E)$ is \emph{undirected} if the binary relation $E$ is symmetric.
\end{defn}
